{\bf {\Large Improving estimates of ecosystem metabolism by reducing effects of tidal advection on dissolved oxygen time series}}

### 2015-05-21 comments.Rnw
revisions proofed

A useful approach for conceptualizing instances when weighted regression may be most appropriate can be described using an ``end member'' paradigm.  These end members are the terminal points of the water mass that is horizontally advected past the \ac{DO} sensor.  One end member is typically characterized by tidal marshes during flood tide, whereas the second end member may be characterized by oxygenated oceanic waters during ebb tide.  An important distinction is made between end members that are influenced by actual biological processes that occur at each terminus and those that are not, where the former case is more likely a common occurrence at locations with large tidal amplitudes.  In the latter case, variation in dissolved oxygen at the \ac{DO} sensor is solely related to physical advection and weighted regression should work as intended provided collinearity with the solar cycle is at a minimum.  For other sites where biological processes affect the \ac{DO} at the end members, the tidal characteristics of a site and the chosen window widths are critical determinants of the ability of weighted regression to isolate the true metabolic signal.  Biological signals from diurnal or semidiurnal tides that exhibit rapid pregression with the solar cycle can be statistically isolated with relatively smaller window widths as the average (i.e., detided) signal can be quantified in fewer tidal cycles.  Conversely, mixed tides that exhibit prolonged periods of synchronicity with the solar cycle, as was observed for Elkhorn Slough, will require larger window widths to characterize the true metabolic signal.   Issues of collinearity at mixed sites add additional challenges as previously noted.  Caution should be used with larger window widths as the potential to oversmooth and mute actual interday variation is increased.  Relatively small window widths that produce noticeable differences in metabolism estimates may have meaningful implications for metabolism, even if interday variation is smoothed.  We conclude that weighted regression has the ability to describe the true metabolic signal regardless of tidal characteristics and biological processes that vary at the end members, although choosing appropriate window widths and evaluating collinearity with the solar cycle are critical factors that must be considered in its application.

>>>>

A useful approach for conceptualizing instances when weighted regression may be most appropriate can be described using an ``end member'' paradigm.  These end members are the terminal points of the water mass that is horizontally advected past the \ac{DO} sensor.  One end member is typically characterized by tidal marshes during flood tide, whereas the second end member may be characterized by oxygenated oceanic waters during ebb tide.  An important distinction is made between end members that are influenced by actual biological processes that occur at each terminus and those that are not, where the former case is more likely a common occurrence at locations with large tidal amplitudes.  In the latter case, variation in dissolved oxygen at the \ac{DO} sensor is solely related to physical advection and weighted regression should work as intended provided collinearity with the solar cycle is minimal.  At sites where biological processes affect \ac{DO} at the end members, the tidal characteristics of a site and the chosen window widths are critical determinants of the ability of weighted regression to isolate the true metabolic signal.  Biological signals from diurnal or semidiurnal tides that exhibit rapid pregression with the solar cycle can be statistically isolated with relatively smaller window widths as the average (i.e., detided) signal can be quantified in fewer tidal cycles.  Conversely, sites with mixed tides that exhibit prolonged synchronicity with the solar cycle, as at Elkhorn Slough, will require larger window widths to characterize the true metabolic signal.  Issues of collinearity at mixed sites add additional challenges as previously noted.  Caution should be used with larger window widths as the potential to oversmooth and mute actual interday variation is increased.  For diurnal and semidiurnal sites, relatively small window widths that produce noticeable differences in estimates may have meaningful implications for interpreting metabolism from filtered time series.  We conclude that weighted regression has the ability to describe the true metabolic signal regardless of tidal characteristics and biological processes that vary at the end members, although chosen window widths and collinearity with the solar cycle affect its application.

### 2015-05-21 discussion.Rnw
revisions proofed

The weighted regression approach was developed to improve estimates of ecosystem metabolism by removing variation associated with tidal change in observed \ac{DO} time series.  The application to simulated \ac{DO} time series with known characteristics and extension to continuous monitoring data from selected \ac{NERRS} sites suggested the approach can isolate and remove a nontrivial amount of variation in observed \ac{DO} from tidal change.  Further, time averages of metabolism estimates using the filtered \ac{DO} time series were significantly different than those using the observed data, particularly for relatively long periods of observation depending on location. These results suggest that previous estimates may not accurately reflect true metabolic signals if the effects of tidal variation confound biological signals in observed \ac{DO} time series.  The regression method and open-water technique may also have broad appeal for application in estuaries that are shallow and vertically-mixed, such as those within \ac{NERRS}.  Extension to stratified systems could be possible, provided water quality time series across depth strata are available.  The open-water technique generally assumes the water column is vertically mixed or that metabolic estimates derived from a surface sensor only apply to the upper layer in a stratified system \citep{Staehr10,Kemp12}.  Vertically-integrated metabolic rates for a stratified system would require estimates from different depths, followed by additional validation to ensure rates agree with expectations.  In particular, application of the open-water method to each depth stratum would require an estimate of gas exchange across the pycnocline, whereas the technique implemented herein relied on a model for air-sea gas exchange at the surface.  Meaningful metabolic estimates could be obtained using such an approach, following the application of weighted regression to remove tidal influences from \ac{DO} time series in each depth layer.

>>>>

The weighted regression approach was developed to improve estimates of ecosystem metabolism by removing variation associated with tidal change in observed \ac{DO} time series.  The application to simulated \ac{DO} time series with known characteristics and extension to continuous monitoring data from selected \ac{NERRS} sites suggested the approach can isolate and remove a significant amount of variation in observed \ac{DO} from tidal change.  Further, time averages of metabolism estimates using the filtered \ac{DO} time series were significantly different than those using the observed data, particularly for relatively long periods of observation depending on location. These results suggest that previous estimates may not accurately reflect true metabolic signals if the effects of tidal variation confound biological signals in observed \ac{DO} time series.  The regression method and open-water technique may also have broad appeal for application in estuaries that are shallow and vertically-mixed, such as those within \ac{NERRS}.  Extension to stratified systems is possible, provided time series across depth strata are available.  The open-water technique assumes the water column is vertically mixed or that estimates from a surface sensor only apply to the upper layer in a stratified system \citep{Staehr10,Kemp12}.  Time series from different depths would be required to estimate metabolic rates that are vertically-integrated, followed by additional validation to ensure rates agree with expectations.  In particular, application of the open-water method to each depth stratum would require an estimate of gas exchange across the pycnocline, whereas the technique implemented herein relied on a model for air-sea gas exchange at the surface.  Meaningful metabolic estimates could be obtained using such an approach, following the application of weighted regression to remove tidal influences.

### 2015-05-21 intro.Rnw
revisions proofed

This article describes the development and application of a method for improving estimates of ecosytem metabolism computed from \ac{DO} time series by reducing the effect of tidal advection on continuous \ac{DO} observations.  We used a weighted regression approach originally developed to resolve trends in pollutant concentrations in streams and rivers \citep{Hirsch10}.  The weighted regression approach creates dynamic predictions of \ac{DO} as a function of time and tidal height change, which are then used to filter, or detide, the \ac{DO} signal.  The model is based on the recognition that daily fluctuations in \ac{DO} caused by metabolism are associated with the solar cycle, whereas other fluctuations in estuaries are likely associated with cyclical water level changes that generally exhibit pregression relative to the solar cycle.  The weighted regression model was applied, rather than methods commonly used for detiding in physical oceanography, to allow for the complex and dynamic patterns of \ac{DO} changes relative to advection.  The method targets the periodicity of the tidal component as a separate parameter during model fitting, which allows the ability to isolate the biological component of the dissolved oxygen time series.  As a result, the weighted regression approach can preserve the true biological signal in the output rather than risking removal of both the biological and physical components as with traditional deconvulution methods.  This approach offers a distinct advantage for estuaries where the magnitude of tidal effects on water quality observations can be severe.  During initial method development, we used simulated \ac{DO} time series with known characteristics to evaluate the ability of the weighted regression to remove the simulated effects of a tidally-advected \ac{DO} gradient.  Subsequently, the simulation results informed further development of the method as applied to four case studies chosen from the \aclu{NERRS} (\acs{NERRS}, \citealt{Wenner04}).  In all examples, tidal height is used as a proxy for advection because it was recorded with the \ac{NERRS} data.  In the absence of quantitative data describing lateral \ac{DO} variation (e.g., contemporaneous stations along a tidal axis), the model determines the advective effect empirically.

>>>>

This article describes the development and application of a method for improving estimates of ecosytem metabolism computed from \ac{DO} time series by reducing the effect of tidal advection on continuous \ac{DO} observations.  We used a weighted regression approach originally developed to resolve trends in pollutant concentrations in streams and rivers \citep{Hirsch10}.  The weighted regression approach creates dynamic predictions of \ac{DO} as a function of time and tidal height change, which are then used to filter, or detide, the \ac{DO} signal.  The model is based on the recognition that daily fluctuations in \ac{DO} caused by metabolism are associated with the solar cycle, whereas other fluctuations in estuaries are likely associated with cyclical water level changes that generally exhibit pregression relative to the solar cycle.  The weighted regression model was applied, rather than methods commonly used for detiding in physical oceanography, to allow for the complex and dynamic patterns of \ac{DO} changes relative to advection.  The method targets the periodicity of the tidal component as an explicit variable during model fitting, which allows the ability to isolate the biological component of the dissolved oxygen time series.  As a result, the weighted regression approach can preserve the true biological signal in the output rather than risking removal of both the biological and physical components as with traditional deconvulution methods.  This approach offers a distinct advantage for estuaries where the magnitude of tidal effects on water quality observations can be severe.  During initial method development, we used simulated \ac{DO} time series with known characteristics to evaluate the ability of the weighted regression to remove the simulated effects of a tidally-advected \ac{DO} gradient.  Subsequently, the simulation results informed further development of the method as applied to four case studies chosen from the \aclu{NERRS} (\acs{NERRS}, \citealt{Wenner04}).  In all examples, tidal height is used as a proxy for advection because it was recorded with the \ac{NERRS} data.  In the absence of quantitative data describing lateral \ac{DO} variation (e.g., contemporaneous stations along a tidal axis), the model determines the advective effect empirically.

### 2015-05-21 mat_proc.Rnw
nearly done with revisions
revisions proofed

For this study, we adapted a weighted regression model to filter \ac{DO} time series for apparent tidal effects.  This model relied heavily on concepts used to develop the \ac{WRTDS} method for estimating pollutant concentrations in streams and rivers \citep{Hirsch10}.  The functional form of the model is:
\begin{equation}\label{funform}
DO_{obs}= \beta_0 + \beta_1 t + \beta_2 H
\end{equation}
where $DO_{obs}$ is a linear function of time $t$ and tidal height $H$.  Time is a continuous variable for the day and time of each observation as a proportion of the number of total observations.  The beginning of each day was defined as the nearest thirty minute observation to sunrise for the location.  Our model differed from the original \ac{WRTDS} method, which included parameters to estimate variation of the response variable on a sinusoidal period.  \ac{DO} variation was not modeled using this approach because the expected metabolically-driven pattern is not strictly sinusoidal.  Tidal height is used as a proxy for advection because the model is empirical and only requires a variable that is correlated with the true measure of interest.  Moreover, tidal height measurements are more widely available and are generally monitored by water quality sondes.

Weighted regression was implemented as a moving window that allowed for estimation of \ac{DO} throughout the time series by adapting to variation through time as a function of tide. Regression models were estimated sequentially for each observation in the time series using dynamic weight vectors that change with the center of the window.  Weight vectors quantified the relevance of observations to the center of the window in respect to time, hour of the day, and tidal height.  Specifically, weights were assigned to each variable using a tri-cube weighting function \citep{Tukey77,Hirsch10}:
\begin{equation}
w= \left\{ 
  \begin{array}{l l}
    \left(1-\left(d/h\right)^3\right)^3 & \quad \textrm{if } |d| \leq h \\
    0 & \quad \textrm{if } |d| > h 
  \end{array} \right.
\end{equation}
where the weight $w$ of each observation is inversely proportional to the distance $d$ from the center of the window such that observations more similar to the point of reference are given higher weight in the regression.  Observations that exceed the maximum width of the window $h$ are assigned a weight of zero.  The tri-cube weighting function is similar to a Gaussian distribution such that weights decrease gradually from the center until the maximum window width is reached.  Regressions that use simpler windows (e.g., boxcar approach) are  more sensitive to influential observations as they enter or leave the window, whereas the tri-cube function minimizes their effect through gradual weighting of observations from the center \citep{Hirsch10}.  The final weight vector for each observation is the product of the three separate weight vectors for time (day), hour, and tidal height. Windows for time and hour are used to weight observations based on distance (time) from the center of the window.  The window for tidal height is used to weight observations based on the difference from mean tide as a proportion of tide range.  For example, a half-window width of 0.5 means that observations are weighted proportionately within +/- 50\% of the tide range referenced to the tidal height in the center of the window. A low weight is given to an observation if any of the three weighting values were not similar to the center of the window since the final weight vector is the product of three weight vectors for each variable (see the link in the \hyperref[multi]{multimedia} section for graphical display of different weights).

>>>>

For this study, we adapted a weighted regression model to filter \ac{DO} time series for apparent tidal effects.  This model relied heavily on concepts used to develop the \ac{WRTDS} method for estimating pollutant concentrations in streams and rivers \citep{Hirsch10}.  The functional form of the model is:
\begin{equation}\label{funform}
DO_{obs}= \beta_0 + \beta_1 t + \beta_2 H
\end{equation}
where $DO_{obs}$ is a linear function of time $t$ and tidal height $H$.  Time is a continuous variable for the day and time of each observation as a proportion of the number of total observations.  The beginning of each day was defined as the nearest thirty minute observation to sunrise for the location.  Our model differed from the original \ac{WRTDS} method, which included parameters to estimate variation of the response variable on a sinusoidal period.  \ac{DO} variation was not modeled using this approach because the expected metabolically-driven pattern is not strictly sinusoidal.

Tidal height is used as a proxy for advection because the model is empirical and only requires a variable that is correlated with the true measure of interest.  An important distinction between tidal height and advection is that each variable could provide different information about a tidal regime.  Tidal heights at the minimum and maximum of the range may be associated with periods of low advection when water masses are not moving rapidly past the sensor, whereas tidal heights near the mean may be more likely to have greater advection.  Accordingly, our use of tidal height should not be confused with a variable that directly measures advection.  The model only requires a variable that indicates a particular point in the tidal cycle, such that tidal height can be mapped to advection with quantifiable periodicity that can be isolated.

Weighted regression was implemented as a moving window that allowed for estimation of \ac{DO} throughout the time series by adapting to variation through time as a function of tide. Regression models were estimated sequentially for each observation in the time series using dynamic weight vectors that change with the center of the window.  Weight vectors quantified the relevance of observations to the center of the window in respect to time, hour of the day, and tidal height.  Specifically, weights were assigned to each variable using a tri-cube weighting function \citep{Tukey77,Hirsch10}:
\begin{equation}
w= \left\{ 
  \begin{array}{l l}
    \left(1-\left(d/h\right)^3\right)^3 & \quad \textrm{if } |d| \leq h \\
    0 & \quad \textrm{if } |d| > h 
  \end{array} \right.
\end{equation}
where the weight $w$ of each observation is inversely proportional to the distance $d$ from the center of the window such that observations more similar to the point of reference are given higher weight in the regression.  Observations that exceed the maximum width of the window $h$ are assigned a weight of zero.  The tri-cube weighting function is similar to a Gaussian distribution such that weights decrease gradually from the center until the maximum window width is reached.  Regressions that use simpler windows (e.g., boxcar approach) are  more sensitive to influential observations as they enter or leave the window, whereas the tri-cube function minimizes their effect through gradual weighting of observations from the center \citep{Hirsch10}.  The final weight vector for each observation is the product of the three separate weight vectors for time (day), hour, and tidal height. Windows for time (continuous throughout the day) and hour (within each day) are used to weight observations based on distance (time) from the center of the window.  The window for tidal height is used to weight observations based on the difference from mean tide as a proportion of tide range.  For example, a half-window width of 0.5 means that observations are weighted proportionately within +/- 50\% of the tide range referenced to the tidal height in the center of the window. A low weight is given to an observation if any of the three weighting values were not similar to the center of the window since the final weight vector is the product of three weight vectors for each variable (see the link in the \hyperref[multi]{multimedia} section for graphical display of different weights).

### 2015-05-21 swmp_noise.Rnw
revisions proofed

% example of error surfaces 
\centering\vspace*{\fill}
<<err_surf1, fig.height = 3.5, fig.width = 5.5, cache = T, echo = F, eval = T, fig.cap = "Heat maps of correlations and errors (\\ac{RMSE}) for filtered \\ac{DO} time series ($DO_{dtd}$) from weighted regression with `true' biological \\ac{DO} ($DO_{bio}$) for varying simulation parameters: strength of tidal association with \\ac{DO} signal ($DO_{adv}$), amount of process uncertainty ($\\varepsilon_{pro}$), amount of observation observation uncertainty ($\\varepsilon_{obs}$), and strength of diel \\ac{DO} component ($DO_{die}$).  Each tile represents the correlation or error from results for a given combination of simulation parameters averaged for all window widths (as in \\cref{fig:err_surf2}).  See \\cref{tab:dtd_perf1} for a summary of results for each unique parameter.">>=

@@

% example of error surfaces 
\centering\vspace*{\fill}
<<err_surf2, fig.height = 2.33, fig.width = 6, cache = T, echo = F, eval = T, fig.cap = "Heat maps of correlations and errors (\\ac{RMSE}) for filtered \\ac{DO} time series ($DO_{dtd}$) from weighted regression with `true' biological \\ac{DO} ($DO_{bio}$) for varying half window widths: days, hour of day, and proportion of tidal range.  Each tile represents the correlation or error from results for a given combination of window widths averaged for all simulation parameters (as in \\cref{fig:err_surf1}).  See \\cref{tab:dtd_perf2} for a summary of results for each unique window.">>=

@@

% plots of summarized metabolism estimates, before/after detiding
% all case studies
\centering\vspace*{\fill}
<<metab_sum, cache = T, eval = T, echo = F, cache = T, fig.height = 5.5, fig.width = 7, fig.cap = 'Means and standard errors of daily metabolism estimates (gross production, total respiration) aggregated by month.  Aggregated estimates are shown for observed and filtered \\ac{DO} time series.  May was removed from Rookery Bay because of incomplete data.'>>=

>>>>

% example of error surfaces 
\centering\vspace*{\fill}
<<err_surf1, fig.height = 3.5, fig.width = 5.5, cache = T, echo = F, eval = T, fig.cap = "Heat maps of correlations and errors (\\ac{RMSE}) for filtered \\ac{DO} time series ($DO_{dtd}$) from weighted regression with `true' biological \\ac{DO} ($DO_{bio}$) for varying simulation parameters: strength of tidal association with \\ac{DO} signal ($DO_{adv}$), amount of process uncertainty ($\\varepsilon_{pro}$), amount of observation observation uncertainty ($\\varepsilon_{obs}$), and strength of diel \\ac{DO} component ($DO_{die}$).  Each tile represents the correlation or error from results for a given combination of simulation parameters averaged for all window widths (as in \\cref{fig:err_surf2}).  See \\cref{tab:dtd_perf1} for a summary of combined results for each unique parameter.">>=

@@

% example of error surfaces 
\centering\vspace*{\fill}
<<err_surf2, fig.height = 2.33, fig.width = 6, cache = T, echo = F, eval = T, fig.cap = "Heat maps of correlations and errors (\\ac{RMSE}) for filtered \\ac{DO} time series ($DO_{dtd}$) from weighted regression with `true' biological \\ac{DO} ($DO_{bio}$) for varying half window widths: days, hour of day, and proportion of tidal range.  Each tile represents the correlation or error from results for a given combination of window widths averaged for all simulation parameters (as in \\cref{fig:err_surf1}).  See \\cref{tab:dtd_perf2} for a summary of combined results for each unique window.">>=

@@

% plots of summarized metabolism estimates, before/after detiding
% all case studies
\centering\vspace*{\fill}
<<metab_sum, cache = T, eval = T, echo = F, cache = T, fig.height = 5.5, fig.width = 7, fig.cap = 'Means and standard errors of daily metabolism estimates (gross production, total respiration) averaged by month.  Averaged results are shown for observed and filtered \\ac{DO} time series.  May was removed from Rookery Bay because of incomplete data.'>>=

### 2015-05-21 swmp_noise.tex
revisions proofed

Tidal height is used as a proxy for advection because the model is empirical and only requires a variable that is correlated with the true measure of interest.  An important distinction between tidal height and advection is that the two variables could provide different information about a tidal regime.  Tidal heights at the minimum and maximum of the range may be associated with periods of low advection when water masses are not moving rapidly past the sensor, whereas tidal heights near the mean may be more likely to have greater advection.  Accordingly, our use of tidal height should not be confused with a variable that is directly proportional to advection.  The model only requires a variable that indicates a particular point in the tidal cycle, such that tidal height can be mapped to advection with quantifiable periodicity that the model can isolate.  Moreover, tidal height measurements are more widely available and are generally monitored by water quality sondes.

@@

The filtered \ac{DO} time series were compared to the simulated data to evaluate the ability of weighted regression to characterize the biological \ac{DO} time series in \cref{do_obs}. Comparisons were made using Pearson correlation coefficients and the \ac{RMSE}.  Overall, the weighted regressions produced filtered time series that were comparable to the `true' biological time series regardless of the simulation parameters (\cref{tab:dtd_perf1}) or window widths (\cref{tab:dtd_perf2}, results for each simulation can be viewed using the link in the \hyperref[multi]{multimedia} section).  The median correlation between the filtered and biological values for all time series and window widths was 0.63, with values ranging from 0.05 (very poor) to 1.00 (perfect).  Mean error was 1.02, with values ranging from 0 (perfect) to 2.12 (very poor).  Simulations with very poor performance were those those with the \ac{DO} signal composed entirely of noise from observation uncertainty. As expected, simulations with no biological or tidal influence had filtered time series that were identical to the true time series (e.g., correlation of one, \ac{RMSE} of zero).

@@

The observed and filtered daily estimates were averaged by month for each site to evaluate the effect of filtering on mean production and respiration at the monthly time scale (\cref{tab:case_res,fig:metab_sum}).  Filtered production and respiration estimates for Padilla Bay and Rookery Bay exhibited monthly variation that was more characteristic of expected trends during warmer months than in the unfiltered estimates.  Results for Sapelo Island suggested that time averaged estimates, either as monthly or annual means, were comparatively unchanged by filtering, although there were some more subtle differences seasonally.  Results for Elkhorn Slough varied significantly such that summer production and respiration were significantly reduced by filtering. It is likely that both the filtered and unfiltered estimates are erroneous; the result of collinearity between the tidal and solar cycle.  Overall, these trends emphasize the importance of considering different averaging periods for interpreting metabolism estimates.  Each case study showed differences in observed and filtered values at monthly aggregations, suggesting tidal variation may influence metabolism estimates at relatively long time scales (\cref{tab:case_res}).

@@

\caption[Heat maps of correlations and errors (\ac{RMSE}) for filtered \ac{DO} time series ($DO_{dtd}$) from weighted regression with `true' biological \ac{DO} ($DO_{bio}$) for varying simulation parameters]{Heat maps of correlations and errors (\ac{RMSE}) for filtered \ac{DO} time series ($DO_{dtd}$) from weighted regression with `true' biological \ac{DO} ($DO_{bio}$) for varying simulation parameters: strength of tidal association with \ac{DO} signal ($DO_{adv}$), amount of process uncertainty ($\varepsilon_{pro}$), amount of observation observation uncertainty ($\varepsilon_{obs}$), and strength of diel \ac{DO} component ($DO_{die}$).  Each tile represents the correlation or error from results for a given combination of simulation parameters averaged for all window widths (as in \cref{fig:err_surf2}).  See \cref{tab:dtd_perf1} for a summary of results for each unique parameter.\label{fig:err_surf1}}
\end{figure}

@@

\caption[Heat maps of correlations and errors (\ac{RMSE}) for filtered \ac{DO} time series ($DO_{dtd}$) from weighted regression with `true' biological \ac{DO} ($DO_{bio}$) for varying half window widths]{Heat maps of correlations and errors (\ac{RMSE}) for filtered \ac{DO} time series ($DO_{dtd}$) from weighted regression with `true' biological \ac{DO} ($DO_{bio}$) for varying half window widths: days, hour of day, and proportion of tidal range.  Each tile represents the correlation or error from results for a given combination of window widths averaged for all simulation parameters (as in \cref{fig:err_surf1}).  See \cref{tab:dtd_perf2} for a summary of results for each unique window.\label{fig:err_surf2}}
\end{figure}

@@

\caption[Means and standard errors of daily metabolism estimates (gross production, total respiration) aggregated by month]{Means and standard errors of daily metabolism estimates (gross production, total respiration) aggregated by month.  Aggregated estimates are shown for observed and filtered \ac{DO} time series.  May was removed from Rookery Bay because of incomplete data.\label{fig:metab_sum}}
\end{figure}

>>>>

Tidal height is used as a proxy for advection because the model is empirical and only requires a variable that is correlated with the true measure of interest.  An important distinction between tidal height and advection is that each variable could provide different information about a tidal regime.  Tidal heights at the minimum and maximum of the range may be associated with periods of low advection when water masses are not moving rapidly past the sensor, whereas tidal heights near the mean may be more likely to have greater advection.  Accordingly, our use of tidal height should not be confused with a variable that directly measures advection.  The model only requires a variable that indicates a particular point in the tidal cycle, such that tidal height can be mapped to advection with quantifiable periodicity that can be isolated.

@@

The filtered \ac{DO} time series were compared to the simulated data to evaluate the ability of weighted regression to characterize the biological \ac{DO} time series in \cref{do_obs}. Comparisons were made using Pearson correlation coefficients and the \ac{RMSE}.  Overall, the weighted regressions produced filtered time series that were reasonable representations of the `true' biological time series regardless of the simulation parameters (\cref{tab:dtd_perf1}) or window widths (\cref{tab:dtd_perf2}, results for each simulation can be viewed using the link in the \hyperref[multi]{multimedia} section).  The median correlation between the filtered and biological values for all time series and window widths was 0.63, with values ranging from 0.05 (very poor) to 1.00 (perfect).  Mean error was 1.02, with values ranging from 0 (perfect) to 2.12 (very poor).  Simulations with very poor performance were those those with the \ac{DO} signal composed entirely of noise from observation uncertainty. As expected, simulations with no biological or tidal influence had filtered time series that were identical to the true time series (e.g., correlation of one, \ac{RMSE} of zero).

@@

The observed and filtered daily estimates were averaged by month for each site to evaluate the effect of filtering on mean production and respiration at the monthly time scale (\cref{tab:case_res,fig:metab_sum}).  Filtered production and respiration estimates for Padilla Bay and Rookery Bay exhibited monthly variation that was more characteristic of expected trends during warmer months than in the unfiltered estimates.  Results for Sapelo Island suggested that time averaged estimates, either as monthly or annual means, were comparatively unchanged by filtering, although there were some more subtle differences seasonally.  Results for Elkhorn Slough varied significantly such that summer production and respiration were significantly reduced by filtering. It is likely that both the filtered and unfiltered estimates are erroneous; the result of collinearity between the tidal and solar cycle.  Overall, these trends emphasize the importance of considering different averaging periods for interpreting metabolism estimates.  Each case study showed differences in observed and filtered values for monthly means, suggesting tidal variation may influence metabolism estimates at relatively long time scales (\cref{tab:case_res}).

@@

\caption[Heat maps of correlations and errors (\ac{RMSE}) for filtered \ac{DO} time series ($DO_{dtd}$) from weighted regression with `true' biological \ac{DO} ($DO_{bio}$) for varying simulation parameters]{Heat maps of correlations and errors (\ac{RMSE}) for filtered \ac{DO} time series ($DO_{dtd}$) from weighted regression with `true' biological \ac{DO} ($DO_{bio}$) for varying simulation parameters: strength of tidal association with \ac{DO} signal ($DO_{adv}$), amount of process uncertainty ($\varepsilon_{pro}$), amount of observation observation uncertainty ($\varepsilon_{obs}$), and strength of diel \ac{DO} component ($DO_{die}$).  Each tile represents the correlation or error from results for a given combination of simulation parameters averaged for all window widths (as in \cref{fig:err_surf2}).  See \cref{tab:dtd_perf1} for a summary of combined results for each unique parameter.\label{fig:err_surf1}}
\end{figure}

@@

\caption[Heat maps of correlations and errors (\ac{RMSE}) for filtered \ac{DO} time series ($DO_{dtd}$) from weighted regression with `true' biological \ac{DO} ($DO_{bio}$) for varying half window widths]{Heat maps of correlations and errors (\ac{RMSE}) for filtered \ac{DO} time series ($DO_{dtd}$) from weighted regression with `true' biological \ac{DO} ($DO_{bio}$) for varying half window widths: days, hour of day, and proportion of tidal range.  Each tile represents the correlation or error from results for a given combination of window widths averaged for all simulation parameters (as in \cref{fig:err_surf1}).  See \cref{tab:dtd_perf2} for a summary of combined results for each unique window.\label{fig:err_surf2}}
\end{figure}

@@

\caption[Means and standard errors of daily metabolism estimates (gross production, total respiration) averaged by month]{Means and standard errors of daily metabolism estimates (gross production, total respiration) averaged by month.  Averaged results are shown for observed and filtered \ac{DO} time series.  May was removed from Rookery Bay because of incomplete data.\label{fig:metab_sum}}
\end{figure}
